\documentstyle[psfig]{letter}
\setlength{\textheight}{9.75in}
\setlength{\footheight}{0.0in}
\setlength{\topmargin}{-0.25in}   % should be 0
\setlength{\headheight}{0.0in}
\setlength{\headsep}{0.0in}
\setlength{\textwidth}{6.6in}
\setlength{\oddsidemargin}{0in}
\setlength{\parindent}{0pc}
\setlength{\parskip}{6pt plus 1.5pt minus 1.5pt}

\name{Margrit Betke}

\signature{\vspace*{-.9cm} Margrit Betke,\\ Associate Professor}

\begin{document}
\pagestyle{empty}

\begin{letter}

%\bucsletterhead
\centerline{\Large Assent Form}
% for subjects between 7 and 18 years

The purpose of this form is to document that assent was obtained from
a person between the ages of 7 and 18 years to participate in a
research study.  If the minor cannot read this form, the statement in
the box below must be read to him or her.

%\vspace*{.5cm}
{\em Title of Research Study:}
Intelligent Interfaces to Empower People with Disabilities to
Participate in the Information Society

%\vspace*{.5cm}

{\em Investigator:} Margrit Betke, Ph.D., Phone: 617-353-6412, Email:
betke@cs.bu.edu

%\vspace*{.5cm}

{\em Location of Testing:}  \rule{3cm}{.01cm}

%\vspace*{.5cm}

\begin{center}
\fbox{
\parbox[t]{5.5in}{

{\em Purpose:} The goal of this project to help people with severe
disabilities use computers.  Our computer has a video camera.  We
would like to test if it can be a tool for you.  Maybe it can help you
communicate with your family and friends.

\vspace*{.1cm}

{\em Procedures:}

\begin{itemize}

\item You will be videotaped in front of the computer.  There may be
up to three computer sessions.  Each can take between 10 to 30
minutes.  There will be a break between sessions, typically a week.

\item During the computer sessions you will be asked to move your
nose, head, or other body parts.  Our computer program, called Camera
Mouse, will track your movements with a video camera and translate
them into the movements of the mouse pointer on the screen.

\item If you can control the mouse pointer with your movements, we
will ask you to play with some computer games and a spelling program.

\end{itemize}

{\em Risks:}  The computer session may be tiring.  We may use lighting for the
videotaping, and sometimes this lighting may be warm.

{\em Benefits:} You may find a new tool for communication and
education.

\vspace*{.3cm}

{\em You do not have to take part in the computer sessions and you can
stop at any time.  If you refuse to participate, you will not lose any
benefits to which your are otherwise entitled. }

\vspace*{.3cm}

You can stop at any time and ask the investigator and her
students questions.

}}
\end{center}

%\hrulefill

\vspace*{.3cm}

I obtained initial assent from the subject, \rule{4cm}{.01cm}, to participate
in this research study.  The subject indicated his/her willingness to
participate in this research study by (e.g.  nodding or blinking or
making a noise):

\vspace{1cm}

Investigator Signature \hrulefill    Date: \hrulefill


\vspace{.5cm}

I, \rule{4cm}{.01cm}, will be monitoring the child to assure that he/she
continues to assent to participate in this research study.  If I
believe that he/she tries to express the desire to stop the test, I
will inform the research team and the computer session will be
terminated immediately.

\vspace{0.5cm}

Witness Signature \hrulefill  Date: \hrulefill

\vspace{0.2cm}

Relationship of witness to subject (e.g., caregiver, parent,
guardian):  \hrulefill

\end{letter}

\end{document} 