\documentstyle[10pt,psfig]{letter}
\setlength{\textheight}{9.5in}
\setlength{\footheight}{0.0in}
\setlength{\topmargin}{0in}   % should be 0
\setlength{\headheight}{0.0in}
\setlength{\headsep}{0.0in}
\setlength{\textwidth}{6.6in}
\setlength{\oddsidemargin}{0in}
\setlength{\parindent}{0pc}
\setlength{\parskip}{6pt plus 1.5pt minus 1.5pt}

\name{Margrit Betke}

\signature{\vspace*{-.7cm} Margrit Betke,\\ Assistant Professor}

\begin{document}
\pagestyle{empty}

\begin{letter}

%\bucsletterhead
\centerline{\Large Informed Consent to Participate in a Research Study }

The purpose of this form is to document that consent was obtained from
a person over 18 years of age to participate in a research study.  If
the person cannot read this form, it must be read to him or her.

%\vspace*{.5cm}
{\em Title of Research Study:}
Intelligent Interfaces to Empower People with Disabilities to
Participate in the Information Society


{\em Investigator:} Margrit Betke, Ph.D., Phone: 617-353-6412, Email:
betke@cs.bu.edu

{\em Purpose:} The objective of this project is to help people with
severe disabilities gain access to a computer and thereby obtain a
tool for communication.  The project will explore methods for
detection, tracking, and interpretation of human body components and
their motion in video.  Computer programs will be developed that use
these interpretations to provide access to commercially available or
custom-built software.

If you agree to participate in this research project, the following
things will happen:

\begin{itemize}
\item You will be videotaped at  \rule{3cm}{.01cm} in at most three computer
sessions, which will take between 10 to 30 minutes.  Typically there
will be one week between each session.

\item During the sessions, you will be asked to control the mouse
pointer on the screen by moving your eyes or by small movements of the
head, toe, thumb, or other body parts.

\item If your are able to control the mouse pointer, we will ask you
to perform a sequence of communication tasks.  The tasks may be
writing a sentence with custom-built spelling software or playing with
educational entertainment software.

\end{itemize}

{\em Confidentiality:}  All information and video data obtained in this
research project will be considered confidential.  It will be used for
research purposes only.  All records will be coded by an id number and
kept in a locked file at Boston University.  Access to the digital
data will be restricted.

{\em Benefits:} Participation in this study introduces you to a new
computer tool for communication and education.

{\em Risks:} The computer session may be tiring.  The risk of exertion
will be minimized by limiting the computer sessions to at most 30
minutes. We may use lighting for the videotaping, and sometimes this
lighting may be warm.


{\em Questions:} The researcher has provided information to you about
this study and has offered to answer your questions.  If you have
questions about your rights as a participant in this research study,
please contact David Berndt, Director of the Charles River Campus
Institutional Review Board, at 617-353-4365.


{\em Right to Refuse or Withdraw:} Your participation in the research
study is entirely voluntary.  You are free to refuse to take part or
withdraw at any time. If you have a physical disability, a caregiver
will have to be present throughout the testing and observe you to
verify that you assent to participate.

{\em Consent:} I,  \rule{5cm}{.01cm}, agree to participate in this research
study.

Signature of Subject \hrulefill  Date: \hrulefill

If subject cannot sign due to his or her physical disability:

Name and Signature of Witness \hrulefill  Date: \hrulefill


\vspace*{.5cm}


Signature of Person Obtaining Consent \hrulefill  Date: \hrulefill

\end{letter}

\end{document} 