\documentstyle[11pt,psfig]{letter}
\setlength{\textheight}{8.5in}
\setlength{\footheight}{0.0in}
\setlength{\topmargin}{0in}   % should be 0
\setlength{\headheight}{0.0in}
\setlength{\headsep}{0.0in}
\setlength{\textwidth}{6.6in}
\setlength{\oddsidemargin}{0in}
\setlength{\parindent}{0pc}
\setlength{\parskip}{6pt plus 1.5pt minus 1.5pt}

\name{Margrit Betke}

\signature{\vspace*{-.7cm} Margrit Betke,\\ Assistant Professor}

\begin{document}
\pagestyle{empty}

\begin{letter}

%\bucsletterhead
\centerline{\Large Video Release Form}

\centerline{\large for Subject over 18 Years}


\vspace*{.5cm}

{\em Title of Research Study:}
Intelligent Interfaces to Empower People with Disabilities to
Participate in the Information Society


{\em Investigator:} Margrit Betke, Ph.D., 617-353-6412,
betke@cs.bu.edu

If you would like to participate in this research study you need to
agree with the first statement below.  If you do not agree with the
second statement you may still participate in the study.

\vspace{.5cm}

%\hfill
%\hrule

{\em 1) I am a participant in the above referenced study.  I agree to
allow the investigators in this study to videotape me for the purposes
of the study.  I understand that the tape will be used only by the
investigators.  The data will be digitized and stored on a secure
computer system at Boston University until August 2010 and then
deleted.  I understand that I have the right to request that the video
data be destroyed at any time.}

%\vspace{.5cm}
Signature of Subject \hrulefill  Date: \hrulefill

If subject cannot sign due to his or her physical disability:

Name and Signature of Witness \hrulefill  Date: \hrulefill

%\vspace{.7cm}

Signature of Person Obtaining Consent \hrulefill  Date: \hrulefill


\vspace{.5cm}


%\hfill
%\hrule

{\em 2) I allow the investigators to retain the video data for future
research and do not request a data deletion date. I allow the
investigators to include pictures or videos of myself in research and
education publications and demonstrations.  I understand that I have
the right to refuse these requests and that I can withdraw my
permission at any time in the future.  I understand that, for any data
released on the Web, it may not be possible to rescind the data
completely.}

%\vspace{.5cm}
Signature of Subject \hrulefill  Date: \hrulefill

If subject cannot sign due to his or her physical disability:

Name and Signature of Witness \hrulefill  Date: \hrulefill

%\vspace{.5cm}
Signature of Person Obtaining Consent \hrulefill  Date: \hrulefill

%\vspace{.5cm}


\end{letter}

\end{document} 